\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{Literature Survey}\label{literature-survey}

\subsubsection{Title: Using Genetic Algorithms to evolve a Neural
Network based Draughts
Player}\label{title-using-genetic-algorithms-to-evolve-a-neural-network-based-draughts-player}

\subsubsection{Student: Thien Nguyen}\label{student-thien-nguyen}

\subsubsection{Academic Advisor: Stefan
Dantchev}\label{academic-advisor-stefan-dantchev}

\subsubsection{Durham University}\label{durham-university}

\section{Background}\label{background}

\begin{quote}
Description: Draughts AI players are currently designed to play at a fixed ability. While it has produced very competitive and intelligent
players, they require tweaks in order to improve its performance. By
combining Neural Networks and Genetic Algorithms, this issue could
possibly be solved by creating a player that can grow in ability over
time.
\end{quote}

\subsection{\#\# Environment}\label{environment}

\subsection{Themes}\label{themes}

\begin{itemize}
\tightlist
\item
  Machine Learning
\item
  Artificial Neural Networks
\item
  Evolutionary Models
\item
  Genetic Algorithms
\item
  Draughts (Checkers)
\end{itemize}

\subsection{Definition of Terms}\label{definition-of-terms}

\textbf{Genetic Algorithm} - An evolutionary method that solves
optimisation problems. This is based on Darwin's theorem of perpetually
evolving populations of solutions.

\textbf{Neural Network} - A computational model based on the operations
of ``interconnected processing elements, which process information by
their dynamic state response to external inputs.'' {[}1{]}

\textbf{Draughts} -

For the sake of clarity these rules will be enforced: - Take Piece. -
Forced Promotion

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Pages 2--4 Important issues of identified themes from results of
reading.

\section{Proposed Direction of the Project (Page
5)}\label{proposed-direction-of-the-project-page-5}

\section{Conclusion (Page 6)}\label{conclusion-page-6}

\section{References}\label{references}

{[}1{]} ``Neural Network Primer: Part I'' by Maureen Caudill, AI Expert,
Feb. 1989

\end{document}
